Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-05-24 Text/Reviews/ResponsesR0R1-Reviewer1.tex

\documentclass[11pt]{report}

\usepackage[pdftex]{geometry}
\geometry{a4paper,left=2.8cm,right=2.8cm,top=1.5cm,bottom=1.5cm,twoside}

\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{graphicx}
	\graphicspath{./Comments/}
\usepackage[many]{tcolorbox}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{subfigure}
\usepackage{bm,bbm}
\usepackage{float}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\newtcolorbox{reviewbox}[1]{
colback = white!5!white,
colframe = purple!75!black,
fonttitle=\bfseries,
title=#1
}

\newtcolorbox{responsebox}[1]{
	colback = white!5!white,
	colframe = white!75!black,
	fonttitle=\bfseries,
	title=#1
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
\large{\textbf{Response Letter to Reviewer \# 1}}

\vglue 0.3cm

\huge{ Identifying Heterogeneity in SAR Data with New Test Statistics\\ (remotesensing-3021303 )}
\end{center}

%\authors
\begin{center}
\textbf{Alejandro C.\ Frery, Janeth Alpala, Abraao D.\ C.\ Nascimento }
\end{center}

\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{2cm}
\noindent Dear Editors
\bigskip

\noindent We are grateful to the reviewers for the valuable comments and the time spent on checking our manuscript. 
We have addressed their comments towards improving the paper contents and presentation. 
Below we detail the changes and updates incorporated into the manuscript in this round of review.

\medskip

%-------------------------------------
\begin{reviewbox}{Comment 1}
Page 2, line 81. When defining L, do you refer to the number of looks or to the equivalent number of looks?

\end{reviewbox}

\begin{responsebox}{Response}

\end{responsebox}

\begin{reviewbox}{Comment 2}
Page 15, line 266. Could you please better define the intensity format? Does it refer to GRD? In that case, which acquisition mode and which final equivalent number of looks? How does this information relates with the L values in Figure 13 caption? It would also be useful to complement the description with the images acquisition date.
\end{reviewbox}

\begin{reviewbox}{Comment 3}
Page 15, Figure 13. In order to ease the interpretation of the results for the 3 sites, it would be useful to show an optical image (the closest's Sentinel-2 available for example) of the corresponding SAR images.
\end{reviewbox}

\begin{reviewbox}{Comment 4}
Page 15, Figure 13 caption. In reference to the L values 18, 36 and 36. Could you please provide more information about how you get those values?
\end{reviewbox}

\begin{reviewbox}{Comment 5}
Page 16, line 269. Could you comment on why you selected a 7x7 window?
\end{reviewbox}

\begin{reviewbox}{Comment 6}
As a suggestion, in order to conduct a more quantitative analysis of the results for each estimator, would you consider comparing the mean and standard deviation values of the different tests among some reference areas in the images? Ideally, a land cover map would serve. Alternatively, you may use some polygons with a clear land cover label (water, vegetation, urban). This would also serve to evaluate the sensitivity of the estimators for classification purposes.
\end{reviewbox}

\begin{reviewbox}{Comment 7}
Some general comments:
\begin{itemize}
	\item in the case you chose an GRD image. Wouldn't it make more sense to apply the operators on an Single Look Complex image so in native SAR coordinates?
	\item could you comment what to expect if doing the same tests employing higher resolution images such as TerraSAR-X's?
	\item could you comment what would be the impact of your work in classification applications with SAR images?
\end{itemize}
\end{reviewbox}

\end{document}

### 2024-05-24 Text/Reviews/ResponsesR0R1-Reviewer2.tex

\vspace{2cm}
\noindent Dear Editors
\bigskip

\noindent We are grateful to the reviewers for the valuable comments and the time spent on checking our manuscript. 
We have addressed their comments towards improving the paper contents and presentation. 
Below we detail the changes and updates incorporated into the manuscript in this round of review.

\medskip

%-------------------------------------
\begin{reviewbox}{Comment 1}
The paper estimates homogeneous areas, and conversely heterogeneous areas, in SAR imagery via speckle statistics by exploiting variations in scattering at the pixel level. Teasing out information from this statistical behavior remains an intricate, delicate process; one which you appear to have accomplished.

I have only a few comments and suggestions for clarification that, hopefully, will enhance the readability \& ultimate applicability of the ideas presented.

1. The 3rd to the last paragraph in the Introduction seems redundant. First entropy is discussed and then the 2 CV estimates, so why return again to entropy? (Perhaps some of this paragraph could be incorporated into the previous entropy discussion.)
\end{reviewbox}

@@

\begin{responsebox}{Response}

\end{responsebox}

\begin{reviewbox}{Comment 2}
2. In Eq. (8), the limit of alpha -> -inf is not transparent. The first 5 terms match eq. (7), and the ln(gamma) \& digamma terms seem to cancel, however, that leaves the ln(-1-alpha) \& L factors. A short discussion, or footnote, would help the reader. 
\end{reviewbox}

\begin{reviewbox}{Comment 3}
3. Fig. 4 Q-Q plots: Are the dashed green lines fits or theoretical estimates of the distributions? What do the different scales imply? (Perhaps a larger variance in one of the distributions?) A short note in the caption or clarification in the text would help. (The later Q-Q plots all show an x=y line for reference. Why the change here?)
\end{reviewbox}

\begin{reviewbox}{Comment 4}
4. What does 'nominal levels of 1\%, 5\%, and 10\%' mean? And, how are these 'achieved' in all cases? This paragraph is the only place where 'nominal levels' are mentioned, please clarify their meaning \& significance.
\end{reviewbox}

\begin{reviewbox}{Comment 5}
The mathematics is, by necessity, a bit dense, therefore I've concentrated my comments on the flow of the paper so that the casual reader may readily follow. To fully follow, comprehend \& replicate this work will require effort on the reader's part, nonetheless clarification of the above points will assist in understanding the gist of the paper. 
\end{reviewbox}

### 2024-05-24 Text/Reviews/ResponsesR0R1-Reviewer2.tex

%-------------------------------------
\begin{reviewbox}{Comment 1}
The paper estimates homogeneous areas, and conversely heterogeneous areas, in SAR imagery via speckle statistics by exploiting variations in scattering at the pixel level. Teasing out information from this statistical behavior remains an intricate, delicate process; one which you appear to have accomplished.

I have only a few comments and suggestions for clarification that, hopefully, will enhance the readability \& ultimate applicability of the ideas presented.

1. The 3rd to the last paragraph in the Introduction seems redundant. First entropy is discussed and then the 2 CV estimates, so why return again to entropy? (Perhaps some of this paragraph could be incorporated into the previous entropy discussion.)
\end{reviewbox}

\begin{responsebox}{Response}
We agree.
We have merged the third-to-last paragraph with the one that discusses the Shannon entropy.
The new paragraph is
\begin{quote}
	\textcolor{blue}{Entropy is a fundamental concept in information theory with far-reaching applications in pattern recognition, statistical physics, image processing, edge detection and SAR image analysis~\cite{Presse2013,MohammadDjafari2015,Avval2021, Nascimento2014,Nascimento2019}. 
		Shannon introduced it in 1948~\cite{Shannon1948} for a random variable to measure information and uncertainty.
		Shannon entropy is a crucial descriptive parameter in statistics, especially for evaluating data dispersion and performing tests for normality, exponentiality and uniformity~\cite{Wieczorkowski1999,Zamanzade2012}. 
		Entropy estimation is challenging, especially when the model is unknown;
		in these cases, non-parametric methods, as those based on spacings~\cite{AlizadehNoughabi2010,Subhash2021}, can be used.
		This strategy is flexible and robust because it does not enforce a model or parametric constraints.
		Different roughness levels, which materialize as different models for SAR data, have different entropy values.
		We designed a bootstrap-improved non-parametric estimator for the Shannon entropy.}
\end{quote}
Please note that the references are correctly numbered and formatted in the revised manuscript.
\end{responsebox}

### 2024-05-24 Text/R1-Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Beginning review

Entropy is a fundamental concept in information theory with far-reaching applications in pattern recognition, statistical physics, image processing, edge detection and SAR image analysis&nbsp;\cite{Presse2013,MohammadDjafari2015,Avval2021, Nascimento2014,Nascimento2019}. 
Shannon introduced it in 1948&nbsp;\cite{Shannon1948} for a random variable to measure information and uncertainty.
Shannon entropy is a crucial descriptive parameter in statistics, especially for evaluating data dispersion and performing tests for normality, exponentiality and uniformity&nbsp;\cite{Wieczorkowski1999,Zamanzade2012}. 
Entropy estimation is challenging, especially when the model is unknown. In these cases, non-parametric methods are used.
Spacing methods have been discussed as a non-parametric approach in Refs.&nbsp;\cite{AlizadehNoughabi2010,Subhash2021}. 
This strategy is flexible and robust because it does not enforce a model or parametric constraints.

@@

The other parameter we study is the Shannon entropy.
Different roughness levels materialized as models for SAR data, have different entropy values, but this fundamental quantity can also be estimated in a model-agnostic way.
We exploit this property and design a bootstrap-improved non-parametric estimator for the Shannon entropy.

@@

The primary models for intensity SAR data include the Gamma and $\mathcal{G}_I^0$  distributions&nbsp;[@Frery1997]. 
The first is suitable for fully-developed speckle and is a limiting case of the second model. This is interesting due to its versatility in accurately representing regions with different roughness properties&nbsp;[@Cassetti2022].
We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim \mathcal{G}_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density
functions (pdfs): 
\begin{align}
    f_Z(z;L, \mu\mid \Gamma_{\text{SAR}})&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z)\label{E:gamma1}\\
    \intertext{ and }
    f_Z(z; \alpha, \gamma, L \mid \mathcal{G}_I^0)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
\end{align} 
where \(\mu > 0\) is the mean, 
\(\gamma > 0\) is the scale, 
\(\alpha < 0\) measures the roughness, 
\(L \geq 1\) is the number of looks, 
\(\Gamma(\cdot)\) is
the gamma function, 
and \(\mathbbm 1_{A}(z)\) is the indicator function
of the set \(A\).

>>>>

Entropy is a fundamental concept in information theory with far-reaching applications in pattern recognition, statistical physics, image processing, edge detection and SAR image analysis&nbsp;\cite{Presse2013,MohammadDjafari2015,Avval2021, Nascimento2014,Nascimento2019}. 
Shannon introduced it in 1948&nbsp;\cite{Shannon1948} for a random variable to measure information and uncertainty.
Shannon entropy is a crucial descriptive parameter in statistics, especially for evaluating data dispersion and performing tests for normality, exponentiality and uniformity&nbsp;\cite{Wieczorkowski1999,Zamanzade2012}. 
Entropy estimation is challenging, especially when the model is unknown;
in these cases, non-parametric methods, as those based on spacings&nbsp;\cite{AlizadehNoughabi2010,Subhash2021}, can be used.
This strategy is flexible and robust because it does not enforce a model or parametric constraints.
Different roughness levels, which materialize as different models for SAR data, have different entropy values.
We designed a bootstrap-improved non-parametric estimator for the Shannon entropy.

@@

@@

The primary models for intensity SAR data include the Gamma and $\mathcal{G}_I^0$  distributions&nbsp;[@Frery1997]. 
The first is suitable for fully-developed speckle and is a limiting case of the second model. This is interesting due to its versatility in accurately representing regions with different roughness properties&nbsp;[@Cassetti2022].
We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim \mathcal{G}_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density
functions (pdfs): 
\begin{align}
    f_Z(z;L, \mu\mid \Gamma_{\text{SAR}})&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z)\label{E:gamma1}\\
    \intertext{ and }
    f_Z(z; \alpha, \gamma, L \mid \mathcal{G}_I^0)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
\end{align} 
where \(\mu > 0\) is the mean, 
\(\gamma > 0\) is the scale, 
\(\alpha < 0\) measures the roughness, 
\(L \geq 1\) is the number of looks (either nominal or estimated, thus not restricted to integer values), 
\(\Gamma(\cdot)\) is
the gamma function, 
and \(\mathbbm 1_{A}(z)\) is the indicator function
of the set \(A\).
